Codes for Final report

Biplav TImalsina
and
Dhurba Neupane

```{r, echo=FALSE,results='hide'}
NS<-read.csv("F:/unr/4th sem/applied regression analysis/Assignments/HW7/NStudy.csv",header = TRUE)
newFullData<-NS[,c(3,4,5,6,7,8)]
newData<-NS[1:100,c(3,4,5,6,7,8)]
attach(newData)

pairs(~Block+Cultivar+NSource+NRate+Seedyield+Year,data=newData, 
   main="ScatterPlot")

par(mfrow=c(1,1))
plot(Year,Seedyield,ylab="Seedyield",xlab="Year")

par(mfrow=c(1,1))
plot(Block,Seedyield,ylab="Seedyield",xlab="Block")

```


```{r}
#Creating all possible subsets
X <- cbind(NRate,Cultivar,Block,Year,NSource)
library(leaps)
b <- regsubsets(as.matrix(X),Seedyield)
rs <- summary(b)
rs
par(mfrow=c(1,1))
library(car)
subsets(b,statistic=c("adjr2"),legend=FALSE)




```


```{r}
#generating fake data pairs(~Block+Cultivar+NSource+NRate+Seedyield+Year,data=newData, 
NS<-read.csv("F:/unr/4th sem/applied regression analysis/Assignments/HW7/NStudy.csv",header = TRUE)
attach(NS)
lm <- glm(formula = Seedyield ~ Block+Cultivar+Year+NRate, data = NS)
summary(lm)
standres<-rstandard(lm)
par(mfrow=c(2,2))
plot(Block,standres, ylab="Standardized Residuals")
plot(Cultivar,standres, ylab="Standardized Residuals")
plot(Year,standres, ylab="Standardized Residuals")
plot(NRate,standres, ylab="Standardized Residuals")
library(car)
vif(lm)



standres<-rstandard(model2)
par(mfrow=c(2,2))
plot(Block,standres, ylab="Standardized Residuals")
plot(Cultivar,standres, ylab="Standardized Residuals")
plot(NSource,standres, ylab="Standardized Residuals")
plot(NRate,standres, ylab="Standardized Residuals")
library(car)
car::mmps(model2, layout=c(3,3))

```


```{r}



CultivarProghorn<-Cultivar=="Pronghorn";
CultivarProghorn[CultivarProghorn==TRUE]<-1;

NRate40<-NRate=="N40"
NRate40[NRate40==TRUE]<-1

NRate80<-NRate=="N80"
NRate80[NRate80==TRUE]<-1

NRate120<-NRate=="N120"
NRate120[NRate120==TRUE]<-1
 

#Yield= 480353.88 + 185.47*Block -265.64*CultivarProghorn -238.1*Year 
	#	+ 407.64* Nrate120 + 60.48*NRate40 + 376.31* NRate90 
error<-rnorm(n=nrow(NS),mean=0,sd=2)


fake_yield<-  480353.88 + 185.47*Block -265.64*CultivarProghorn -238.1*Year	+ 407.64* NRate120 + 60.48*NRate40 + 376.31* NRate80 +error
fake_lm <- glm(formula = fake_yield ~ Block+Cultivar+Year+NRate, data = NS)
summary(fake_lm)

car::mmps(fake_lm, layout=c(3,3))

```

SAS Code:
PROC IMPORT DATAFILE="/folders/myfolders/wombat/NStudy.csv"
		    OUT=WORK.MYEXCEL
		    DBMS=CSV
		    REPLACE;
RUN;

/*model1*/
proc genmod data= WORK.MYEXCEL  descending;
class  NRate (ref="N00") Cultivar(ref="Pronghorn") NSource(ref="N1") Block(ref="1") Year(ref="2016");
model Seedyield = Block Cultivar NRate NSource Year; 
run;

/*model1-block*/
proc genmod data= WORK.MYEXCEL  descending;
class  NRate (ref="N00") Cultivar(ref="Pronghorn") NSource(ref="N1") Block(ref="1") Year(ref="2016");
model Seedyield =  Cultivar NRate NSource Year; 
run;

/*model1-cultivar*/
proc genmod data= WORK.MYEXCEL  descending;
class  NRate (ref="N00") Cultivar(ref="Pronghorn") NSource(ref="N1") Block(ref="1") Year(ref="2016");
model Seedyield = Block  NRate NSource Year; 
run;

/*model1-year*/
proc genmod data= WORK.MYEXCEL  descending;
class  NRate (ref="N00") Cultivar(ref="Pronghorn") NSource(ref="N1") Block(ref="1") Year(ref="2016");
model Seedyield = Block Cultivar NRate  Year; 
run;

/*model1-NRate*/
proc genmod data= WORK.MYEXCEL  descending;
class  NRate (ref="N00") Cultivar(ref="Pronghorn") NSource(ref="N1") Block(ref="1") Year(ref="2016");
model Seedyield = Block Cultivar NSource Year; 
run;

/*model2*/
proc genmod data= WORK.MYEXCEL  descending;
class  NRate (ref="N00") Cultivar(ref="Pronghorn") NSource(ref="N1") Block(ref="1") Year(ref="2016");
model Seedyield =  BLock Cultivar NRate NSource; 
run;

/*model2-Block*/
proc genmod data= WORK.MYEXCEL  descending;
class  NRate (ref="N00") Cultivar(ref="Pronghorn") NSource(ref="N1") Block(ref="1") Year(ref="2016");
model Seedyield = Cultivar NRate  NSource; 
run;

/*model1-NSource*/
proc genmod data= WORK.MYEXCEL  descending;
class  NRate (ref="N00") Cultivar(ref="Pronghorn") NSource(ref="N1") Block(ref="1") Year(ref="2016");
model Seedyield = Block Cultivar NRate ; 
run;


/*model2-Cultivar*/
proc genmod data= WORK.MYEXCEL  descending;
class  NRate (ref="N00") Cultivar(ref="Pronghorn") NSource(ref="N1") Block(ref="1") Year(ref="2016");
model Seedyield =  NSource BLock NRate; 
run;

/*model2-nRate*/
proc genmod data= WORK.MYEXCEL  descending;
class  NRate (ref="N00") Cultivar(ref="Pronghorn") NSource(ref="N1") Block(ref="1") Year(ref="2016");
model Seedyield =  NSource Block Cultivar ; 
run;

/*model2-Nsource*/
proc genmod data= WORK.MYEXCEL  descending;
class  NRate (ref="N00") Cultivar(ref="Pronghorn") NSource(ref="N1") Block(ref="1") Year(ref="2016");
model Seedyield =  Block NRate Cultivar; 
run;

/*final model*/
proc genmod data= WORK.MYEXCEL  descending;
class  NRate (ref="N00") Cultivar(ref="Pronghorn") NSource(ref="N1") Block(ref="1") Year(ref="2016");
model Seedyield =  Cultivar NRate NSource Block; 
run;

/*for final model 2*/
```{r}

BlockR<-factor(Block)
CultivarR<-factor(Cultivar,level=c("Pronghorn","BlaineCreek"))
model2<-glm(formula = Seedyield ~ BlockR+CultivarR+NRate+NSource, data = NS)
summary(model2)
vif(model2)
```

